---
title: "CommunicationTiming"
author: "bhollenStats"
date: "February 22, 2018"
output: html_document
runtime: shiny
params:
  xmitFilename: "./data/20200226_CVS_AZMW_Xmit.csv"
  recvFilename: "./data/20200226_CVS_AZMW_Recv.csv"
  maxXmitTime: 500
  xmitPlotMinX: 99.75
  xmitPlotMaxX: 100.25
  xmitBinWidth: 0.01
  respPlotMinX: 0.35
  respPlotMaxX: 0.91
  respBinWidth: 0.01
  maxDeltaT: 200
  minDeltaT: 0.01
  maxRecvT: 100
  minRecvT: 0
---

**OVERVIEW**

  I want a way to analyze the timing of Wireshark collected data for a specific network
  command between a device and its driver.  In the example here I'm evaluating the
  AWRT response from a device.  I collected the data with Wireshark through a testing
  sequence and I want to export the packet dissections from the command transmissions
  and receptions so that I can:

    1. Evaluate the timing between the transmitted request for new data with with AWRT K0 command
    2. Evaluate the response time of the device between the perception of the transmitted AWRT K0
       commad and the receipt of the online data from the device

**PREREQUISITES**

    1. Using packet dissections from WireShark version 2.2.6 (but I don't expect change from different verions)
    2. Column names in the packet dissections are expected to be: {
         "No.",
         "Time",
         "Source",
         "Destination",
         "Protocol",
         "Length",
         "Info"}
    3. I have filtered the packets to provide packet dissections for the transmitted and received commands as:
         Transmission of "AWRT K0" using "data.data contains 02:20:41:57:52:54:20:4B"
         Reception of "AWRT e" using "data.data contains 02:20:41:57:52:54:20:30" (expecting error to be zero (0))

**INPUT BEING ANALYZED**

  The transmit result file is `r params$xmitFilename` and the receive result file is `r params$recvFilename`

```{r xmit_recv_Packets, include=FALSE, cached=FALSE, error=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)

xmitPackets <- read.csv(file = params$xmitFilename)
recvPackets <- read.csv(file = params$recvFilename)
```

Now clean up the data so that they can be joined. I've assumed that each transmit line will match
to a subsequent response line, so I plan to join the data based on that online 'transaction.'

With this resulting table I can calculate the time different (deltaT) between the transmitted
command and the response from the device.

```{r clean_and_tidy, echo=FALSE, cached=FALSE, error=FALSE, warning=FALSE}
library(dplyr)

xmitData <- xmitPackets %>%
  mutate(PacketNo = row_number(), XmitTimeMs = Time * 1000) %>%
  rename(XmitSeqNo = 'No.') %>%
  select(PacketNo, XmitSeqNo, XmitTimeMs)

recvData <- recvPackets %>%
  mutate(PacketNo = row_number(), RecvTimeMs = Time * 1000) %>%
  rename(RecvSeqNo = 'No.') %>%
  select(PacketNo, RecvSeqNo, RecvTimeMs)

transactionData <- xmitData %>%
  inner_join(recvData, by = 'PacketNo') %>%
  mutate(recvDeltaTms = RecvTimeMs - XmitTimeMs) %>%
  mutate(xmitDeltaTms = XmitTimeMs - lag(XmitTimeMs, default=XmitTimeMs[1])) %>%
  select(PacketNo, XmitSeqNo, RecvSeqNo, XmitTimeMs, RecvTimeMs, recvDeltaTms, xmitDeltaTms)

head(transactionData)

```

I first needed to know how reliable the requests for online data were to the device.  I collected `r transactionData %>% count()` measurements and found only `r transactionData %>% filter(xmitDeltaTms > params$maxXmitTime) %>% count()` were greater than `r params$maxXmitTime` milliseconds.  Here are the summary results for all measurements that were less than or equal to `r params$maxXmitTime` milliseconds:

```{r transmitDeltaT_Summary, echo=FALSE, cache=FALSE, comment=""}
justDeltaT <- transactionData %>%
  filter(xmitDeltaTms <= params$maxDeltaT) %>% 
  filter(xmitDeltaTms >= params$minDeltaT) %>%
  select(xmitDeltaTms)
justDeltaT %>%
  summary()
```

Here is the distribution of the measurement data that I collected and analyzed for time between online requests:

```{r transmitDeltaT_plot, echo=FALSE, cached=FALSE}
library(ggplot2)

justDeltaT %>%
  ggplot(aes(x=xmitDeltaTms)) +
  geom_histogram(binwidth = params$xmitBinWidth, show.legend = FALSE, color='darkgreen', fill='green') +
  coord_cartesian(xlim = c(params$xmitPlotMinX, params$xmitPlotMaxX)) +
  labs(x = '[milliseconds]',
       y = '',
       title = 'Time Measurements Between Online Requests within the Device Driver') +
  theme_dark()

```

I also wanted to know how responsive the device was to the request of the online command.  I collected `r count(transactionData)` measurements and found only `r transactionData %>% filter(recvDeltaTms > 20) %>% select(recvDeltaTms) %>% arrange(desc(recvDeltaTms)) %>% count()` that were larger than 20 milliseconds!  Here are the summary results for all measurements that were collected:

```{r onlineResponseTimes_Summary, echo=FALSE, cache=FALSE, comment=""}
onlineResponseTimes <- transactionData %>%
  filter(recvDeltaTms <= params$maxRecvT) %>% 
  filter(recvDeltaTms >= params$minRecvT) %>%
  select(recvDeltaTms)

onlineResponseTimes %>% summary()
```

Here is the distribution of the measurement data that I collected and analyzed for the online response times:

```{r onlineResponseResults, echo=FALSE, cached=FALSE}
temp <- fivenum(onlineResponseTimes$recvDeltaTms)
minX <- (0.5*(temp[2]-temp[1]))
maxX <- temp[4]+(0.5*(temp[5]-temp[4]))
maxX <- 2.5

onlineResponseTimes %>%
  ggplot(aes(x=recvDeltaTms)) +
  geom_histogram(binwidth = params$respBinWidth, show.legend = FALSE, fill='green', color='darkgreen') +
  coord_cartesian(xlim = c(minX, maxX)) +
  labs(x = '[milliseconds]',
       y = '',
       title = 'Response Time Measurements for Online Request',
       subtitle = 'Measurement of time between the request for and receipt of data from the device.') +
  theme_dark()
```

